Incorporating dive behaviour into models of marine animal movement

### 2018-10-04 manuscript/manuscript_template.Rmd
Use citr package for citations

date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
csl: mee.csl
#bibliography: references.bib
header-includes:
   - \usepackage{lineno}
   - \linenumbers
---

```{r, echo=FALSE}
  # devtools::install_github("cboettig/knitcitations@v1")
  library(knitcitations); cleanbib()
  cite_options(citation_format = "pandoc", check.entries=TRUE)
  library(bibtex)
```

@@

The relationship was first described by @Halpern_2006. However, there are also opinions
that the relationship is spurious [@Keil_2012].
We used R for our calculations [@R_Core_Team_2016], and we used package `knitcitations` [@Boettiger_2017] to make the bibliography.

@@

```{r, warning=FALSE, message=FALSE, echo=FALSE} 
  #write.bibtex(file="references.bib")
```

>>>>

date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
csl: mee.csl
bibliography: references.bib
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
fontsize: 12pt
---

```{r, echo=FALSE}
  require(citr)
```

@@

The relationship was first described by @Halpern_2006. However, there are also opinions
that the relationship is spurious [@Keil_2012].
We used R for our calculations [@R_Core_Team_2016], and we used package.

@@
